Coherent IR-Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-29 paper.tex
data availability statement
deleted useless words

@@

\section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
 To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
 The output polarizations under the electric dipole approximation are written as

>>>>

\section{Data Availability Statement}
The workup scripts that support this study are permissively licensed and available for reuse at \href{https://osf.io/2amkq/}{https://osf.io/2amkq/}.

@@

\section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
 To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
 The output polarizations under the electric dipole approximation are written as
